\section{Project Charter}

%%%%%%%%%%%%%%%%%%%%%%%%%%Bibliography %%%%%%%%%%%%%%%
\textbf{Date:} 10/18/2021\\
\textbf{Project Name:} Omnidirectional Ground Penetrating Radar(GPR) Robot 
\textbf{Project Manager:} Sanjib Lamichhane\\
\textbf{Project Tracking Number:} N/A \\
\\
\textbf{Project Justification(problem or opportunity addressed):}\\
Our project will eliminate the need for manual scanning by providing an autonomous, omnidirectional robotic platform.\\
\\
\textbf{Overview of Deliverable(high-level, broad-brush only):}\\
Omnidirectional Robot Prototype of size 17”x17”x6”, and weight of 30 lbs, Product expenses within \$500, Robotic Platform Running on Python Environment, Operation Voltage within 12 - 24 Volts, Speed : 1.5 m/s, Object detection
\\\\
\textbf{Specific Project Objectives \& Success Criteria(schedule, cost, quality):}\\
To develop an autonomous, omnidirectional robotic platform for a GPR antenna, a four-wheeled omnidirectional chassis including a PCB for control systems and power distribution, as well as the software-driven control and path navigation functionality will be built by the end of May 20th, 2022 within the allocated funds of \$500.\\
\\
\textbf{Primary Stakeholders \& Toles (including a broad statement of roles and responsibilities of all customers, sponsors, contributors, reviewers, managers, sign-off authorities, project manager, etc.):}\\
Professor Xiao, the head of the robotics research lab, and Professor Baurin, the faculty advisor for the department of Electrical Engineering at City College are mentoring us in product development and project management respectively. The evaluation of results will be reviewed by the mentors. The design engineers are Sanjib Lamichhane, Daniel Bloom, Qiang Gao, Miguel James, Zu Xiaoke Liu, who are working on the research and development of the robotic platform. Sanjib Lamichhane is also the project manager.\\
\\
\textbf{Key Assumptions(including a broad statement of sponsor/stakeholder inputs and resources to be provided, as well as a delineation of “what’s outside” project scope):}
\\
The GPR antenna as well as the mechanical components such as the omnidirectional wheels will provided by Prof. Xiao’s robotics lab at City College. Our product is expected to be autonomous. It is important to note that the GPR post-processing software is outside the scope of this project.\\
\\
\textbf{Signatures:}The following people agree that the above information is accurate:\\
\textbf{Project Team Members:}\\Sanjib Lamichhane, Miguel James, Daniel Bloom, Zu Qiang Gao, Xiaoke Liu\\
\textbf{Project Sponsor and/or authorizing manager(s):} Prof. Jizhong Xiao, Prof. Edward Baurin\\
\\
