\section{Requirements}

The need of the potential customers are external requirements and the expectations of stakeholders and team members are considered as the internal requirements.
\subsection{External Requirements}
The primary external requirement of our design is to have an automated  ground scanning facility available on an ground-penetrating radar robot. Our priority is to develop a minimum viable prototype that performs the following:
\begin{itemize}
	\item Operating Condition: Indoor, following lab safety protocols.
	\item Temperature: Room Temperature
	\item Surfaces: Smooth, non-inclined floors
	\item Network: Wireless LAN
	\item Size: 17" x 17" x 6"
	\item Weight: 30lbs including wheels, motors, and drivers.
\end{itemize}

\subsection{Internal Requirements}
The internal requirements of the company are divided into Marketing and Manufacturing as follows:\\\\

\textbf{Marketing}
\subsubsection{Market} There are many possible options for these demands. Military applications include detection of unexplored ordnance and detecting tunnels. Archaeology applications include detecting and mapping subsurface archaeological artifacts. Construction Companies can use them to investigate underground substances \cite{andrews1999research}.

\subsubsection{Competition: WaveSense}
Wavesense develops ground penetrating radar for vechicles and robots. The ground penetrating radar technology is used for the localization for autonomous vechicles in any condition. Since, a ground-penetrating radar is unaffected by snow, heavy rain, fog or poor lane markings, GPR can significantly reduce navigation failure rates and assist self-driving functionality \cite{wavesense2020}. \\
As our product performs all these functions in essence, we consider Wave-sense as our competitor.

\subsubsection{Time to market} The minimum viable prototype will be developed by May 2022. The product will be ready to manufacturing phase afterwards. 

\subsubsection{Niche} Our product will be specialized for underground scanning, and the niche market is the construction and manufacturing industry.

\subsubsection{Necessary advertising resources}Upon completion of the first phase (prototype development), we would publish our papers about the product, which will serve as our technical advertisement.Professor Xiao will help us in the publication.  Additionally, information about the product will be published in the social medias for the general public.\\\\

\textbf{Manufacturing}
\subsubsection{Purchasing} The wheels will be provided by Professor Xiao. The Department of Electrical Engineering at City College will provide us funding to purchase motors, drivers, and boards.

\subsubsection{Fabrication} Fabrication technologies such as 3D printing can be used for robot frames and general structures that keep it together. The 3D printing facility in the Robotics Club Lab at City College will be used for this purpose.

\subsection{Assembly} The hardware tools at Robotics lab will be used for the assembly of the products.
